---
title: "Reproducible Research - Peer Assessment 1"
output: html_document
---

The goal of this project is to analyze an individual's activity via the data from their fitness tracker.

First, we need to load the data and create a daily version of the data. 

```{r}
##Load data
activitydata <- read.csv("~/Documents/Learning/R/reproducibleresearch/rrproj1/activity.csv",header=TRUE, na.strings="NA")

##Create new dataframe with steps aggregated by date
dailydata <- aggregate(activitydata$steps,by=list(activitydata$date),sum)
colnames(dailydata) <- c("date","steps")
```

## What is the mean total number of steps taken per day?

1. Histogram of the total number of steps taken each day
```{r}
hist(dailydata$steps,xlab="Steps",main="Steps Histogram")
```

2. Mean and median total number of steps taken per day
```{r}
##Mean
mean(dailydata$steps,na.rm=TRUE)

##Median
median(dailydata$steps, na.rm=TRUE)
```

## What is the average daily pattern?

1. Time-series plot of the 5-minute interval and the average number of steps taken

2. Which 5 minute interval (across all days) contains the maximum number of steps?

## Imputing missing values

1. The total number of missing values in the dataset (rows with NA)

2. Filling in missing values

3. Create new filled in dataset

4. Histogram, mean, and median of new dataset.

## Are there differences in activity patterns between weekdays and weekends?

1. Create a new factor variable in the dataset with two levels - "weekday" / "weekend"

2. Time series panel plot of average steps taken by 5-minute interval (by weekend/weekday)

